Transformer-Based Reranking \\for Improving Korean Morphological Analysis System

### 2023-12-29 contents/draft.tex
Add Author Biography

    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Republic of Korea}}}
    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}}
    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}. \email{nash@jbnu.ac.kr}}
    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}

@@

    \section*{Acknowledgments}
    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)

@@

>>>>

    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Rep. of Korea}}}
    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Rep. of Korea}}}
    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Rep. of Korea}}. \email{nash@jbnu.ac.kr}}
    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}

@@

    \section*{Acknowledgments}
    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human).

@@

    \section*{Author Biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Jihee Ryu} received his BS degree in computer science \& engineering from Chungnam National University, Daejeon, Rep. of Korea, in 2006. He received his MS degree in computer science from KAIST, Daejeon, Rep. of Korea, in 2010. He is currently a senior researcher at ETRI, Daejeon, Rep. of Korea. His research interests include natural language processing, deep learning, and knowledge graph completion.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Soojong Lim} received his BS degree in mathematics from Yonsei University, Seoul, Rep. of Korea, in 1997. He also received his MS degree and PhD in computer science from Yonsei University, in 1998 and 2014, respectively. He is currently a principal researcher at ETRI, Daejeon, Rep. of Korea. His research interests include natural language processing, deep learning, and large language \& crossmodal model.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Oh-Woog Kwon} received his BS degree in computer engineering from Kyungpook National University, Rep. of Korea, in 1992, his MS degree in computer science from KAIST, Rep. of Korea, in 1995, and his PhD degree in computer engineering from the Pohang University of Science and Technology (POSTECH), Rep. of Korea, in 2001. Since 2004, he has been working with the Language Intelligent Research Section, Electronics and Telecommunications Research Institute (ETRI), Daejeon, Rep. of Korea, where he is currently a Director. His major research interests include natural language processing, large language models, and mathematical reasoning.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Seung-Hoon Na} received his PhD degree in computer science from POSTECH in 2008. Currently, he is a professor in Dept. of Computer Science at Jeonbuk National University. Previously, he was a senior researcher at Electronics and Telecommunications Research Institute, Rep. of Korea, after he worked in School of Computing at Natural University of Singapore. His research interests include natural language processing, information retrieval, and machine learning.}
    \end{biography}
